---
title: "Time Series Analysis"
author: "Naveen Kaushik"
date: "9/20/2019"
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=3, fig.align="center")
```

The dataset used is in the file `dataset.xlsx`. The dataset is of Footwear and other personal accessory retailing fpr Australia Capital Territory and the dataset can be found [here](https://www.abs.gov.au/AUSSTATS/abs@.nsf/DetailsPage/8501.0Jul%202019?OpenDocument).


We start with installing the required libraries. 

```{r, message=F}
library(fpp2)
library(readxl)
library(dplyr)
```

Then we would need to read our data into a time series object.

```{r}
myts <- read_xlsx("dataset.xlsx", skip=3) %>%
  pull("29620163") %>%  ts(start = c(1982,4), frequency = 12)
```


We would now plot our series to see how it looks like.

```{r, message=F, warning=F}
autoplot(myts) +
  xlab("Year") +
  ylab("$ Millions") +
  ggtitle("Footwear and other personal accessory retailing")
```

The fpp2 library has functions to plot the seasonal and subseries plots as well. 

```{r, message=F, warning=F}
ggseasonplot(myts, year.labels=TRUE, year.labels.left=TRUE) +
  xlab("Months") +
  ylab("$ Millions") +
  ggtitle("Footwear and other personal accessory retailing")
```

```{r, message=F, warning=F}
ggsubseriesplot(myts) +
  xlab("Months") +
  ylab("$ Millions") +
  ggtitle("Footwear and other personal accessory retailing")
```






